Impact of engines scheduler on the performance of Big Data pipelines in HPC

### 2021-01-21 latex/paper.tex
First write for the datasets section

\section{Methods}
\subsection{Infrastructure} % TODO
\subsection{Dataset} % TODO

>>>>

\section{Methods}
\subsection{Infrastructure} % TODO

\subsection{Dataset}
We used BigBrain\cite{Amunts:13}, a 3-D image of the human brain with voxel intensity ranging between 0 and 65,535.
We converted the blocks into the NIfTI format, a popular format in neuroimaging.
We left the NIfTI blocks uncompressed, resulting in a total data size of \SI{00}{\giga\byte}\MD{Verify the size of the dataset when Lustre back on}.
To evaluate the effect of block size, we resplit these blocks into 30, 125 and 750 blocks of \MD{size for each block segment}, using the \href{https://github.com/big-data-lab-team/sam}{sam} library.

We also used the dataset provided by the Consortium for Reliability and Reproducibility (\href{http://fcon_1000.projects.nitrc.org/indi/CoRR/html/}{CoRR}) \cite{zuo2014open}.
This dataset is freely available on \href{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}{datalad}.
The entire dataset is \SI{408.4}{\giga\byte}, containing anatomical, diffusion and functional images of 1,397 subjects acquiredin 29 sites.
We used all 3,491 anatomical images, representing \SI{39}{\giga\byte} overall (\SI{11.17}{\mega\byte} per image on average).
